Model-based pretreatment for regression with correlated variables.

### 2014-04-07 www/article13.tex
bic*
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@505 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

		Variables in $\boldsymbol{X_1}$ are supposed to be independent.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.
	\subsection{Penalization of the integrated likelihood} \label{compstruct}
  To obtain the marginal regression model we need $S$, the linear structure between the covariates.
	Our full generative generative model allows us to compare structures with criterions like the Bayesian Information Criterion ($BIC$) which penalize the log-likelihood according to the complexity of the structure~\cite{BIChuard}. We will prefer this kind of comparison criterion instead of cross-validation that is very time-consuming and thus not friendly with combinatory problematics.
	We note $\Theta$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|X)&\propto& P(X|S)P(S) \\
		-2\log P(X|S)&\approx & BIC=-2\mathcal{L}(X,S,\Theta)+|\Theta|\log(n)\\  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
	But we can imagine to use other criterions, like the $RIC$ (Risk Inflation Criterion \cite{foster1994risk}) that choose a penalty in $\log p$ instead of $\log n$ and thus gives more parsimonious models when $p$ is larger than $n$ (high dimension) or any other criterion \cite{george1993variable} thought to be better in a given context. 
\\	
		We will now use the following notation: $\psi(S)=\psi(X|S)$	where $\psi(X|S)$ is the chosen criterion, that will be $BIC$ with hierarchical uniform hypothesis in our numerical results. We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.

>>>>

		Variables in $\boldsymbol{X_1}$ are supposed to be independent.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.
	\subsection{Penalization of the integrated likelihood} \label{compstruct}
  To obtain the marginal regression model we need $S$, the linear structure between the covariates.
  Cross-validation is very time-consuming and thus not friendly with combinatory problematics. Moreover, we need a criterion compatible with structures of different sizes (varying $p_2$) and not related with $Y$ because the structure is inherent to $\boldsymbol{X}$ only. Thus it must be a global criterion. 	
	Our full generative generative model allows us to compare structures with criterions like the Bayesian Information Criterion ($BIC$) which penalize the log-likelihood of the joint law on $\boldsymbol{X}$ according to the complexity of the structure~\cite{BIChuard}.

	We note $\boldsymbol{\Theta}$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|X)&\propto& P(X|S)P(S) \\
		-2\log P(X|S)&\approx & BIC=-2\mathcal{L}(X,S,\Theta)+|\Theta|\log(n)\\  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
	But we can imagine to use other criterions, like the $RIC$ (Risk Inflation Criterion \cite{foster1994risk}) that choose a penalty in $\log p$ instead of $\log n$ and thus gives more parsimonious models when $p$ is larger than $n$ (high dimension) or any other criterion \cite{george1993variable} thought to be better in a given context. 
\\	
		We will now use the following notation: $\psi(S)=\psi(X|S)$	where $\psi(X|S)$ is the chosen criterion, that will be $BIC$ with hierarchical uniform hypothesis in our numerical results. We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.
